Differentially Private Bayesian Inference

### 2018-04-09 main.tex
update dilation proof

\begin{equation*}
\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = e^{\lambda} \hat{s}] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.
\end{lem}

@@

\begin{itemize}
	\item $\lambda > 0$
	\begin{itemize}
		\item $u(x,r) > 0$

@@

		\item $u(x,r) < 0$

		% This need to be discuss further.
		We can have:
		\begin{equation*}
		\lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
		\end{equation*}

	\end{itemize}
	\item $\lambda < 0$
	\begin{itemize}
		\item $u(x,r) > 0$

		% This need to be discuss further.
		We can have:
		\begin{equation*}
		\lambda\geq \ln (1 - \frac{S(x)}{\hat{s}}) 
		\end{equation*}
		Since $\lambda > 0$ is the pre-condition, it can be inferred that the property cannot hold under this case.

		\item $u(x,r) < 0$

@@

In conclusion, the dilation property holds under these conditions that: $\lambda u(x,r) > 0$ or $\lambda > 0, u(x,r) < 0, \lambda \leq \ln (1 - \frac{S(x)}{\hat{s}})$.

>>>>

\begin{equation*}
\underset{z \thicksim \expomech}{Pr}[u(z) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r) = e^{\lambda} \hat{s}] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.
\end{lem}

@@

\begin{itemize}
	\item $\lambda > 0$
	\begin{itemize}
		\item $u(r) > 0$

@@

		\item $u(r) < 0$

		% This need to be discuss further.
		% We can have:
		% \begin{equation*}
		% \lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
		% \end{equation*}

	\end{itemize}
	\item $\lambda < 0$
	\begin{itemize}
		\item $u(r) > 0$

		% This need to be discuss further.
		% We can have:
		% \begin{equation*}
		% \lambda\geq \ln (1 - \frac{S(x)}{\hat{s}}) 
		% \end{equation*}
		% Since $\lambda > 0$ is the pre-condition, it can be inferred that the property cannot hold under this case.

		\item $u(r) \leq 0$

@@

% In conclusion, the dilation property holds under these conditions that: $\lambda u(x,r) > 0$ or $\lambda > 0, u(x,r) < 0, \lambda \leq \ln (1 - \frac{S(x)}{\hat{s}})$.

In our case, we are using $-\hlg(\bysinfer(x),r)$ for utility function, we only need to consider the case $u(r) \leq 0$.

Because $\hat{s} = u(r)$ where $r \thicksim \expomech$, we can substitute $\hat{s}$ with $u(\expomech)$. Then, what we need to proof under the event $G = \{\lambda > 0, u(r) \leq 0\}$ is:
\begin{equation*}
u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
\end{equation*}
By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with:
\begin{equation*}
\begin{split}
Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))}{|\mathcal{R}_{OPT}| exp(\epsilon OPT_{u(x)}/2 S(x))}\\
\end{split}
\end{equation*}
In our Bayesian Inference mechanism, the size of the candidate set $\mathcal{R}$ is equal to the size of observed data set plus 1, i.e., $n + 1$, and $OPT_{u(x)} = 0$, then we have:
\begin{equation*}
\begin{split}
Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
\end{split}
\end{equation*}

When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.
